\begin{enumerate}[label=\thesubsection.\arabic*,ref=\thesubsection.\theenumi]
\item Assume that in a family, each child is equally likely to be a boy or a girl. A family with three children is chosen at random. The probability that the eldest child is a girl given that the family has at least one girl is
\begin{enumerate}
\item $\frac{1}{2}$
\item $\frac{1}{3}$
\item $\frac{2}{3}$
\item $\frac{4}{7}$
\end{enumerate}
\input{exemplar/12/13/3/77/assignment7.tex}
\item State whether the statement is True or False. The probabilities that a typist will make 0, 1, 2, 3, 4, 5 or more mistakes in typing a report are, respectively, 0.12, 0.25, 0.36, 0.14, 0.08, 0.11.\\
\solution
\input{exemplar/11/16/3/32/main.tex}
\item State which of the following are not the probability distributions of a random
variable. Give reasons for your answer.
\begin{multicols}{2}  %
 \begin{enumerate}
		 \setlength{\itemsep}{1ex}
  \item
\input{ncert/12/13/4/1/tables/table1_1.tex}

 \item
	\resizebox{0.95\columnwidth}{!}{%
 \input{ncert/12/13/4/1/tables/table1_2.tex}
		 }
\item
  \input{ncert/12/13/4/1/tables/table1_3.tex}
\item
	\resizebox{0.95\columnwidth}{!}{%
  \input{ncert/12/13/4/1/tables/table1_4.tex}
		 }
\end{enumerate}
\end{multicols}  %
\solution
\input{ncert/12/13/4/1/main.tex}
\item A die has two faces each with number ‘1’, three faces each with number ‘2’ and one face with number ‘3’. If die is rolled once, determine
\begin{enumerate}
\item $\pr{2}$
\item $\pr{1 \text{ or } 3}$
\item $\pr{\text{not } 3}$
\end{enumerate}
		\solution
\input{ncert/11/16/4/3/axioms.tex}
\item A die marked 1, 2, 3 in red and 4, 5, 6 in green is tossed. Let A be the event,‘the number is even,’ and B be the event, ‘the number is red’. Are A and B independent?
	\\
\solution
\input{ncert/12/13/2/5/main.tex}
\item  A fair coin and an unbiased die are tossed. Let $A$ be the event 'head appears on the coin' and $B$ be the event '3 on the die'. Check whether $A$ and $B$ are independent events or not.
		\label{ncert/12/13/2/4}
\item A child's game has 8 triangles of which 3 are blue and rest are red, and 10 squares of which 6 are blue and rest are red. One piece is lost at random. Find the probability that it is a
\begin{enumerate}
\item triangle 
\item square 
\item square of blue colour 
\item triangle of red colour           
\end{enumerate}
\solution
\input{exemplar/10/13/3/37/assign3.tex}
\item Suppose you have two coins which appear identical in your pocket. You know
that one is fair and one is 2-headed. If you take one out, toss it and get a head,
what is the probability that it was a fair coin?
\\
\input{exemplar/12/13/3/32/main.tex}
\item A box has 5 blue and 4 red balls. One ball is drawn at random and not replaced. Its colour is also not noted. Then another ball is drawn at random. What is the probability of second ball being blue?
	\\
\solution
\input{exemplar/12/13/3/18/main.tex}
\item A bag contains 4 white and 5 black balls. Another bag contains 9 white and 7 black balls. A ball is transferred from the first bag to the second and then a ball is drawn at random from the second bag. Find the probability that the ball drawn is white.
\item An item is manufactured by three machines A, B and C. Out of the total number of items manufactured during a specified period, $50\%$ are manufactured on A, $30\%$ on B and $20\%$ on C, $2\%$ of the items produced on A and $2\%$ of items produced on B are defective, and $3\%$ of these products produced on C are defective. All the items are stored at one godown. One item is drawn at random and is found to be defective. What is the probability that is was manufactured on machine A?
\\
\solution
\input{exemplar/12/13/3/48/main.tex}
\item There are two bags, one which contains 3 black balls and 4 white balls while the other contains 4 black balls and 3 white balls. A die is thrown. If it shows up 1 or 3, a ball is taken from the first bag; but it shown up any other number, a ball is taken from the second bag. Find the probability of choosing a black ball.
\\
\solution
\input{exemplar/12/13/3/45/main.tex}
\item A shopkeeper sells three types of flower seeds $A_1, A_2$ and $A_3$. They are sold as a mixture where the proportions are 4:4:2 respectively. The germination rates of the three types of seeds are 0.45, 0.60 and 0.35. Calculate the probability
\begin{enumerate}
\item of a randomly chosen seed to germinate
\item that it will not germinate given that the seed is of type $A_3$,
\item that it is of the type $A_2$ given that a randomly chosen seed does not germinate.
\end{enumerate}
\solution
\input{exemplar/12/13/3/43/main.tex}
\end{enumerate}
