\begin{enumerate}[label=\thesection.\arabic*,ref=\thesection.\theenumi]
	\item A team of medical students doing their internship have to assist during surgeries
at a city hospital. The probabilities of surgeries rated as very-complex, complex,
routine, simple or very-simple are respectively, 0.15, 0.20, 0.31, 0.26, .08. Find
the probabilities that a particular surgery will be rated
\begin{enumerate}
\item complex or very-complex
\item neither very-complex nor very simple
\item routine or complex
\item routine or simple
\end{enumerate}
		\solution
		%\input{exemplar/11/16/3/8/main.tex}
	\item One urn contains two black balls (labelled B1 and B2) and one white ball. A
	second urn contains one black ball and two white balls (labelled W1 and W2).
	Suppose the following experiment is performed. One of the two urns is chosen
	at random. Next a ball is randomly chosen from the urn. Then a second ball is
	chosen at random from the same urn without replacing the first ball.
	
	\begin{enumerate}
	\item What is the probability that two black balls are chosen?
	
	\item What is the probability that two balls of opposite colour are chosen?
	\end{enumerate}
	\solution
	%\input{exemplar/11/16/3/12/main1.tex}
  
\item Suppose an integer from 1 through 1000 is chosen at random, find the probability that the integer is a multiple of 2 or a multiple of 9.
%\input{exemplar/11/16/3/3/main.tex}
\item State whether the statement is True or False.\\
The probability that a person visiting a zoo will see the giraffe is 0.72, the probability that he will see the bears is 0.84 and the probability that he will see both is 0.52.\\
\solution
\\
%\input{exemplar/11/16/3/30/main.tex}
\item State whether the statement is True or False. The probabilities that a typist will make 0, 1, 2, 3, 4, 5 or more mistakes in typing a report are, respectively, 0.12, 0.25, 0.36, 0.14, 0.08, 0.11.\\
\solution
\\
%\input{exemplar/11/16/3/32/main.tex}
\item If A and B are two candidates seeking admission in an engineering College. The probability that A is selected is 0.5 and the probability that both A and B are selected is atmost 0.3. Is it possible that the probability of B getting selected is 0.7?\\
%\input{exemplar/11/16/3/33/main.tex}
\item Let $E_1$ and $E_2$ be two independent events such that $\pr{E_1} = p_1 $ and $ \pr{E_2} = p_2 $ \ Describe in words the events whose probabilities are: 
\begin{enumerate}
\item \ $p_1 p_2$
\quad\item \ $(1 - p_1) p_2 $
\quad\item \ $1 - (1 - p_1)(1 - p_2)$
\quad\item \ $p_1 + p_2 - 2p_1 p_2$
\end{enumerate}
%\input{exemplar/12/13/3/9/main.tex}
\item Suppose that 6\% of the people with blood group O are left handed and 10\% of those with other blood groups are left handed 30\% of the people have blood group O. If a left handed person is selected at random, what is the probability that he/she will have blood group O?
%\input{exemplar/12/13/3/33/main.tex}
\item %\input{exemplar/11/16/3/43/main.tex}
\item If $\pr{A}$ = $\frac{2}{5}$,$\pr{B}$ = $\frac{3}{10}$ and $\pr{AB}$ =$ \frac{1}{5}$, then $\pr{A^{\prime}|B^{\prime}}$.$\pr{B^{\prime}|A^{\prime}}$ is equal to \\
\begin{enumerate}[label=(\Alph*)]
\item 
$\frac{5}{6}$\\
\item 
$\frac{5}{7}$\\
\item 
$\frac{25}{42}$\\
\item 
$1$
%\input{exemplar/12/13/3/59/prob5.tex}
\end{enumerate}
\item $A$ and $B$ are two events such that $\pr{A}= \frac{1}{2}$ , $\pr{B}= \frac{1}{3}$ and $\pr{AB}= \frac{1}{4}$.\\
Find:
\begin{enumerate}[label =\roman*]
\item $\pr{A|B}$  \item $\pr{B|A}$  \item $\pr{A^{\prime}|B}$  \item $\pr{A^{\prime}|B^{\prime}}$
\end{enumerate}
\solution:\\
%\input{exemplar/12/13/3/7/main.tex}
\item If $\pr{A} = \frac{3}{10}, \pr{B} = \frac{2}{5}$ and $\pr{A+B} = \frac{3}{5}$, then $\pr{\left. B \right| A} + \pr{\left. A \right| B} $ equals
\begin{enumerate}
	\item $\frac{1}{4}$ \vspace{2pt}
	\item $\frac{1}{3}$ \vspace {2pt}
	\item $\frac{5}{12}$ \vspace{2pt}
	\item $\frac{7}{12}$ \vspace{2pt}
\end{enumerate}
%\input{exemplar/12/13/3/58/main.tex}
\item The probability distribution of a discrete random variable X is given below. The value of k is equal to:
\begin{table}[!ht]
%\input{exemplar/12/13/3/87/tables/Book1.tex}
\end{table}
\begin{enumerate}[label=(\alph*)]
\item 8
\item 16
\item 32
\item 48
\end{enumerate}
%\input{exemplar/12/13/3/87/main.tex}
\item state True or False for the given statement:
Two independent events are always mutually exclusive.\\
\solution \\
%\input {exemplar/12/13/3/97/main.tex}
\item If A and B are two events and A $\ne \phi$, B $\ne \phi$, then
\begin{enumerate}
	\item $\pr{A|B} = \pr{A}.\pr{B}$
	\item $\pr{A|B} = \frac{\pr{A\cap B}}{\pr{B}}$
	\item $\pr{A|B}.\pr{B|A} = 1$
	\item $\pr{A|B} = \frac{\pr{A}}{\pr{B}}$
\end{enumerate}
%\input {exemplar/12/13/3/62/main.tex}
\item Let $A$ and $B$ be two  events such that $\pr{A} = \frac{3}{8}$, $\pr{B} = \frac{5}{8}$ and $\pr{A+B} = \frac{3}{4}$. Then $\pr{\left.{A}|\right.{B}}.\pr{\left.{A^\prime} |\right.{B}}$ is equal to
\begin{enumerate}[label=(\alph*)]
\item $\frac{2}{5}$
\vspace{3pt}
\item $\frac{3}{8}$
\vspace{3pt}
\item $\frac{3}{20}$
\vspace{3pt}
\item $\frac{6}{25}$
\end{enumerate}
%\input{exemplar/12/13/3/71/main(2).tex}
\item If $P(A)=0.4$, $P(B)=0.8$ and $P(B|A)=0.6$, then $P(A \cup B)$ is equal to
\begin{enumerate}
\item 0.24
\item 0.3
\item 0.48
\item 0.96
\end{enumerate}
\solution
%\input{exemplar/12/13/3/61/main.tex}
\item If A and B aret two events such that \pr{A} =$\frac{1}{2}$ \pr{B} =$\frac{1}{3}$, \pr{A|B}=$\frac{1}{4}$, Then \pr{A' B'} equals
\begin{enumerate}
	\item $\frac{1}{12}$
	\item $\frac{3}{4}$
	\item $\frac{1}{4}$
	\item $\frac{3}{16}$	
\end{enumerate}
\solution
%\input{exemplar/12/13/3/60/main.tex}
\item If $A$ and $B$ are such events that $\pr{A} > 0$ and $\pr{B}\neq 1$, then $\pr{A^\prime|B^\prime}$ is
\begin{enumerate}
\item $1-\pr{A|B}$
\item $1-\pr{A^\prime|B}$
\item $\frac{1-\pr{A+B}}{\pr{B^\prime}}$
\item $\frac{\pr{A^\prime}}{\pr{B^\prime}}$
\end{enumerate}
%\input{exemplar/12/13/3/68/main.tex}
\item  Two events $E$ and $F$ are independent. If $\pr{E} = 0.3$, $\pr{E+F} = 0.5$, then $\pr{E|F}-\pr{F|E}$ equals
\begin{enumerate}
    \item[(a)] $\frac{2}{7}$
    \item[(b)] $\frac{3}{35}$
    \item[(c)] $\frac{1}{70}$
    \item[(d)] $\frac{1}{7}$
\end{enumerate}
\solution
%\input{exemplar/12/13/3/73/main.tex}
\item You are given that A and B are two events such that \pr{B}=$\frac{3}{5}$ \pr{A \ | \ B}=$\frac{1}{2}$ \pr{A+B}=$\frac{4}{5}$ and \pr{A}=$\frac{1}{2}$  \pr{B \ | \ A^\prime} is equal to\\
%\input{exemplar/12/13/3/65/main.tex}
\item If $A$ and $B^\prime$ are independent events, then $\pr{A^\prime+B}=1-\pr{A}\pr{B^\prime}$.\\
%\input{exemplar/12/13/3/100/main.tex}
\item If A and B are two events such that $\pr{A|B}=p,\pr{A}=p,\pr{B}=\frac{1}{3}$ and $\pr{A+B}=\frac{5}{9}$,then $p=$\\
\solution
%\input{exemplar/12/13/3/104/main.tex}
\item If $A$ and $B$ are two events such that $\pr{A} > 0$ and $\pr{A} + \pr{B} > 1$, then 
\begin{align*}
    \pr{B | A} \geq 1 - \frac{\pr{B^\prime}}{\pr{A}}
\end{align*}
\solution
%\input{exemplar/12/13/3/102/main.tex}
\item If 
\begin{align}
\pr{B} = \frac{3}{5},
\pr{A|B} = \frac{1}{2} \text{and}
\pr{A + B} = \frac{4}{5}, \text{then}
\pr{A + B}^{\prime} + \pr{A^{\prime} + B}
\end{align}
\solution
%\input{exemplar/12/13/3/66/main.tex}
\item Let $A$ and $B$ be two events. If 
\begin{align}
\pr{A|B} = \pr{A},
\end{align} 
then $A$ is of $B$.\\
\solution
%\input{exemplar/12/13/3/108/main.tex}
\item

 If \pr{A|B} $>$ \pr{A}, then which of the following is correct :

\begin{enumerate}[label=(\Alph*)]

 \item  
 \label{12.13.6.18.A}
 \pr{B|A} $<$ \pr{B}\\
 \item 
  \label{12.13.6.18.B}
 \pr{AB} $<$ \pr{A}\pr{B}\\
 \item 
 \label{12.13.6.18.C}
 \pr{B|A} $>$ \pr{B}\\
 \item 
  \label{12.13.6.18.D}
 \pr{B|A} = \pr{B}\\

 \end{enumerate}
%\input{ncert/12/13/6/18/main1.tex}
\item Let  and B be independent events with \pr{A} = 0.3 and \pr{B} = 0.4. Find 
\begin{enumerate}
\item \pr{AB} \item \pr{A+B}

\item \pr{A|B} \item \pr{B|A}
\end{enumerate}
\solution
%\input{ncert/12/13/2/8/main.tex}
\item Compute \pr{A|B} , if \pr{B} = 0.5 and \pr{AB} = 0.32.\\
	\solution
	%\input{ncert/12/13/1/2/main.tex}
	%
\item A fair die is rolled. Consider events $E=1,3,5,\, F=2,3$ and $G=2,3,4,5$. Find
\begin{enumerate}
\item $\pr{E \mid F} \text{ and } \pr{F \mid E}$
\item $\pr{E \mid G} \text{ and } \pr{G \mid E}$
\item $\pr{{E \cup F} \mid G} \text{ and } \pr{{E \cap F} \mid G}$
\end{enumerate}
%
\solution
%\input{ncert/12/13/1/11/main.tex}
	\item If A and B are two events such that $P(A) \neq 0$ and $P\brak{B\mid A} = 1$, then
\begin{enumerate}
\item $A \subset B$\\
\item $B\subset A$\\
\item $B = \phi$\\
\item $A = \phi$\\
\end{enumerate}
		\solution
		%\input{ncert/12/13/6/17/main.tex}
	\item If \pr {A \mid B} $>$ \pr{A}, then which of the following is correct 
\begin{enumerate}
 \item \pr{B\mid A} $<$ \pr{(B)} \\
 \item \pr{AB} $<$ \pr{A}  \pr{B}  \\
 \item \pr{B\mid A} $>$ \pr{B} \label{eq:ncert/12/13/6/18/c}\\ 
 \item \pr{B\mid A} $=$ \pr{B} \\
\end{enumerate}
		\solution
		%\input{ncert/12/13/6/18/main.tex}
\item You are given that A and B are two events such that $\pr{B}=\frac{3}{5},\pr{A|B}=\frac{1}{2}$ and $\pr{A+B}=\frac{4}{5}$,then $\pr{A}$ equals\\
\solution
%\input{exemplar/12/13/3/64/main.tex}
	\item If $A$ and $B$ are any two events such that \pr{A}+\pr{B}-\pr{AB}=\pr{A}, then choose the correct option
\begin{enumerate}
\item  $\pr{B|A}=1$
\item $\pr{A|B}=1$
	\label{prob:12/13/6/19}
\item $\pr{B|A}=0$
\item $\pr{A|B}=0$
\end{enumerate}
		\solution
		%\input{ncert/12/13/6/19/main.tex}
\item Three events A, B and C have probabilities $\frac{2}{5}$,$\frac{1}{3}$ and $\frac{1}{2}$ respetively.Given that $\pr{AC}=\frac{1}{5}$ and $\pr{BC}=\frac{1}{4}$,find the values of $\pr{C | B}$ and $\pr{A^{\prime} C^{\prime}}$\\
\solution
%\input{exemplar/12/13/3/8/main.tex}
\item Two Coins are tossed once, where\\
\brak{i} E : Tail appears on one coin,\qquad F : one coin shows head\\
\brak{ii}  E : no tail appears,\qquad\qquad\qquad F : no head appears
Determine \pr{E\mid F}.
%\input{ncert/12/13/1/7a/ncertmain.tex}
%
\end{enumerate}
