Choose the correct answer in the following exercises
\begin{enumerate}[label=\thesubsection.\arabic*,ref=\thesubsection.\theenumi]
%\begin{enumerate}[resume*]
\item The probability of obtaining an even prime number on each die, when a pair of dice is rolled is
\begin{enumerate}
\item 0
\item $\frac{1}{3}$
\item $\frac{1}{12}$
\item $\frac{1}{36}$
\end{enumerate}
\item State which of the following are not the probability distributions of a random
variable. Give reasons for your answer.
 \begin{enumerate}
  \item
\begin{table}[h! ]
 \caption{}
\label{tab:ncert/12/13/4/1/1}
%\input{ncert/12/13/4/1/tables/table1_1.tex}
 \end{table}
 
 \item
\begin{table}[h! ]
  \label{tab:ncert/12/13/4/1/2}
  \caption{}
  %\input{ncert/12/13/4/1/tables/table1_2.tex}
\end{table}

\item
\begin{table}[h]
  \caption{}
  \label{tab:ncert/12/13/4/1/3}
  %\input{ncert/12/13/4/1/tables/table1_3.tex}
\end{table}

\item
\begin{table}[h]
  \caption{}
  \label{tab:ncert/12/13/4/1/4}
  %\input{ncert/12/13/4/1/tables/table1_4.tex}
\end{table}
\end{enumerate}
\solution
%\input{ncert/12/13/4/1/main.tex}
\item If a leap year is selected at random, what is the chance that it will contain 53 tuesdays?
	\\
		\solution
		%\input{ncert/12/13/6/8/axioms.tex}
	\item Assume that the chances of a patient having a heart attack is $40\%$. It is also assumed that a meditation and yoga course reduce the risk of heart attack by $30\%$ and prescription of certain drug reduces its chances by $25\%$. At a time a patient can choose any one of the two options with equal probabilities. It is given that after going through one of the two options the patient selected at random suffers a heart attack. Find the probability that the patient followed a course of meditation and yoga?
	\\
		\solution
		%\input{ncert/12/13/6/13/main.tex}
	\item An electronic assembley consists of two subsystems,say A and B.From previous testing procedures, the following probabilities are assumed to be known
\begin{align}
\pr{\text{A fails}}&=0.20
\\ \pr{\text{B alone fails}}&=0.15
\\ \pr{\text{A  and B fails}}&=0.15
\end{align}
 Evaluate the following probabilities
 \begin{enumerate}
 \item $\pr{\text{A fails given B has failed}}$
 \item $\pr{\text{A fails alone}}$
\end{enumerate}
		\solution
		%\input{ncert/12/13/6/15/main.tex}
  \item
  In a hostel, 60\% of the students read Hindi newspaper, 40\% read English
newspaper and 20\% read both Hindi and English newspapers. A student is
selected at random.
\begin{enumerate}
\item Find the probability that she reads neither Hindi nor English newspapers.
\item If she reads Hindi newspaper, find the probability that she reads English
newspaper.
\item If she reads English newspaper, find the probability that she reads Hindi
newspaper.
\end{enumerate}
\solution
%\input{ncert/12/13/2/16/main.tex}
%
\item If the probabilities for A to fail in an examination is 0.2 and that for B is 0.3, then
the probability that either A or B fails is
\begin{enumerate}
\item $>0.5$
\item 0.5
\item $\le 0.5$
\item 0
\end{enumerate}
\solution
%\input{exemplar/11/16/3/27/main.tex}
\item It is given that in a group of 3 students, the probability of 2 students not having the same birthday is 0.992. What is the probability that the 2 students have the same birthday?
	\\
\solution
\input{ncert/10/15/1/7/main.tex}
\item In a lottery, a person choses six different natural numbers at random from 1 to 20, and if these six numbers match with the six numbers already fixed by the lottery committee, he wins  the prize. What is the probability of winning the prizes in the game? [Hint : order of the numbers is not important.]
	\\
\solution
\input{ncert/11/16/3/11/main.tex}
%
\item  In class XI of a school 40\% of the students study Mathematics and 30\% study Biology. 10\% of the class study both Mathematics and Biology. If a student is selected at random from the class,find the probability that he will be studying Mathematics or Biology
	\\
	\solution
%\input{ncert/11/16/3/18/axioms.tex}
\item In an entrance test that is graded on the basis of two examinations, the probability of a randomly chosen student passing the first examination is 0.8 and the probability of passing the second examination is 0.7. The probability of passing atleast one of them is 0.95. What is the probability of passing both$?$
	\\
	\solution
%\input{ncert/11/16/3/19/main.tex}
 \item In a class of 60 students, 30 opted for NCC, 32 opted for NSS and 24 
    opted for both NCC and NSS. If one of these students is selected at random, 
    find the probability that
    \begin{enumerate}
        \item The student opted for NCC or NSS.
        \item The student has opted neither NCC nor NSS.
        \item The student has opted NSS but not NCC.
    \end{enumerate}
	\solution
%\input{ncert/11/16/3/21/axioms.tex}
\item A die has two faces each with number ‘1’, three faces each with number ‘2’ and one face with number ‘3’. If die is rolled once, determine
\begin{enumerate}
\item $\pr{2}$
\item $\pr{1 \text{ or } 3}$
\item $\pr{\text{not } 3}$
\end{enumerate}
		\solution
%\input{ncert/11/16/4/3/axioms.tex}
\item A die marked 1, 2, 3 in red and 4, 5, 6 in green is tossed. Let A be the event,‘the number is even,’ and B be the event, ‘the number is red’. Are A and B independent?
	\\
\solution
%\input{ncert/12/13/2/5/main.tex}
\item  A fair coin and an unbiased die are tossed. Let $A$ be the event 'head appears on the coin' and $B$ be the event '3 on the die'. Check whether $A$ and $B$ are independent events or not.
		\label{ncert/12/13/2/4}
		\item  A die marked 1, 2, 3 in red and 4, 5, 6 in green is tossed. Let $A$ be the event, 'the number is even, ' and $B$ be the event, 'the number is red'. Are $A$ and $B$ independent?
		\label{ncert/12/13/2/5}
\item Probability of solving specific problem independently by A and B are $\frac{1}{2}$ and $\frac{1}{3}$ respectively. If both try to solve the problem independently, find the probability that
		\label{ncert/12/13/2/13}
\begin{enumerate}
\item the problem is solved
\item exactly one of them solves the problem
\end{enumerate}
\solution
%\input{ncert/12/13/2/14/main.tex}
\item One card is drawn at random from a well shuffled deck of 52 cards. In which of the following cases are the events $E$ and $F$ independent ?
		\label{ncert/12/13/2/14}
\begin{enumerate}
\item $E$: 'the card drawn is spade'\\
$F$: 'the card drawn is an ace'
\item $E$: 'the card drawn is black’\\
$F$ : 'the card drawn is a king’
\item $E$ : 'the card drawn is a king or queen’\\
$F$ : 'the card drawn is a queen or jack’
\end{enumerate}
\solution
%\input{ncert/12/13/2/15/main.tex}
\end{enumerate}
