\begin{enumerate}[label=\thesection.\arabic*,ref=\thesection.\theenumi]
	\item An electronic assembley consists of two subsystems,say A and B.From previous testing procedures, the following probabilities are assumed to be known
\begin{align}
\pr{\text{A fails}}&=0.20
\\ \pr{\text{B alone fails}}&=0.15
\\ \pr{\text{A  and B fails}}&=0.15
\end{align}
 Evaluate the following probabilities
 \begin{enumerate}
 \item $\pr{\text{A fails given B has failed}}$
 \item $\pr{\text{A fails alone}}$
\end{enumerate}
		\solution
		\input{ncert/12/13/6/15/main.tex}
  \item
  In a hostel, 60\% of the students read Hindi newspaper, 40\% read English
newspaper and 20\% read both Hindi and English newspapers. A student is
selected at random.
\begin{enumerate}
\item Find the probability that she reads neither Hindi nor English newspapers.
\item If she reads Hindi newspaper, find the probability that she reads English
newspaper.
\item If she reads English newspaper, find the probability that she reads Hindi
newspaper.
\end{enumerate}
\solution
\input{ncert/12/13/2/16/main.tex}
	\item Assume that the chances of a patient having a heart attack is $40\%$. It is also assumed that a meditation and yoga course reduce the risk of heart attack by $30\%$ and prescription of certain drug reduces its chances by $25\%$. At a time a patient can choose any one of the two options with equal probabilities. It is given that after going through one of the two options the patient selected at random suffers a heart attack. Find the probability that the patient followed a course of meditation and yoga?
	\\
		\solution
		\input{ncert/12/13/6/13/main.tex}
	\item A team of medical students doing their internship have to assist during surgeries
at a city hospital. The probabilities of surgeries rated as very-complex, complex,
routine, simple or very-simple are respectively, 0.15, 0.20, 0.31, 0.26, .08. Find
the probabilities that a particular surgery will be rated
\begin{enumerate}
\item complex or very-complex
\item neither very-complex nor very simple
\item routine or complex
\item routine or simple
\end{enumerate}
		\solution
		%\input{exemplar/11/16/3/8/main.tex}
	\item One urn contains two black balls (labelled B1 and B2) and one white ball. A
	second urn contains one black ball and two white balls (labelled W1 and W2).
	Suppose the following experiment is performed. One of the two urns is chosen
	at random. Next a ball is randomly chosen from the urn. Then a second ball is
	chosen at random from the same urn without replacing the first ball.
	
	\begin{enumerate}
	\item What is the probability that two black balls are chosen?
	
	\item What is the probability that two balls of opposite colour are chosen?
	\end{enumerate}
	\solution
	%\input{exemplar/11/16/3/12/main1.tex}
  
\item Suppose an integer from 1 through 1000 is chosen at random, find the probability that the integer is a multiple of 2 or a multiple of 9.
%\input{exemplar/11/16/3/3/main.tex}
\item State whether the statement is True or False.\\
The probability that a person visiting a zoo will see the giraffe is 0.72, the probability that he will see the bears is 0.84 and the probability that he will see both is 0.52.\\
\solution
\\
%\input{exemplar/11/16/3/30/main.tex}
\item State whether the statement is True or False. The probabilities that a typist will make 0, 1, 2, 3, 4, 5 or more mistakes in typing a report are, respectively, 0.12, 0.25, 0.36, 0.14, 0.08, 0.11.\\
\solution
\\
%\input{exemplar/11/16/3/32/main.tex}
\item If A and B are two candidates seeking admission in an engineering College. The probability that A is selected is 0.5 and the probability that both A and B are selected is atmost 0.3. Is it possible that the probability of B getting selected is 0.7?\\
%\input{exemplar/11/16/3/33/main.tex}
\item Let $E_1$ and $E_2$ be two independent events such that $\pr{E_1} = p_1 $ and $ \pr{E_2} = p_2 $ \ Describe in words the events whose probabilities are: 
\begin{enumerate}
\item \ $p_1 p_2$
\quad\item \ $(1 - p_1) p_2 $
\quad\item \ $1 - (1 - p_1)(1 - p_2)$
\quad\item \ $p_1 + p_2 - 2p_1 p_2$
\end{enumerate}
%\input{exemplar/12/13/3/9/main.tex}
\item Suppose that 6\% of the people with blood group O are left handed and 10\% of those with other blood groups are left handed 30\% of the people have blood group O. If a left handed person is selected at random, what is the probability that he/she will have blood group O?
%\input{exemplar/12/13/3/33/main.tex}
\item %\input{exemplar/11/16/3/43/main.tex}
\item Two Coins are tossed once, where\\
\brak{i} E : Tail appears on one coin,\qquad F : one coin shows head\\
\brak{ii}  E : no tail appears,\qquad\qquad\qquad F : no head appears
Determine \pr{E\mid F}.
%\input{ncert/12/13/1/7a/ncertmain.tex}
\item A fair die is rolled. Consider events $E=1,3,5,\, F=2,3$ and $G=2,3,4,5$. Find
\begin{enumerate}
\item $\pr{E \mid F} \text{ and } \pr{F \mid E}$
\item $\pr{E \mid G} \text{ and } \pr{G \mid E}$
\item $\pr{{E \cup F} \mid G} \text{ and } \pr{{E \cap F} \mid G}$
\end{enumerate}
%
\solution
%\input{ncert/12/13/1/11/main.tex}
\end{enumerate}
