\begin{enumerate}[label=\thesubsection.\arabic*,ref=\thesubsection.\theenumi]
\item A box contains 5 red marbles, 8 white marbles and 4 green marbles. One marble is taken
out of the box at random. What is the probability that the marble taken out will be 
\begin{multicols}{3}
\begin{enumerate}
    \item red ? 
    \item white ? 
    \item  not green?
\end{enumerate}
\end{multicols}
\solution
\input{ncert/10/15/1/9/multinom.tex}
\item A box contains 10 red marbles, 20 blue marbles and 30 green marbles. 5 marbles
are drawn from the box, what is the probability that
\begin{enumerate}
\item all will be blue?
\item atleast one will be green?
\end{enumerate}
\solution
%\input{ncert/11/16/4/1/multinom.tex}
\item A box of oranges is inspected by examining three randomly selected oranges drawn without replacement. If all the three oranges are good, the box is approved for sale, otherwise, it is rejected. Find the probability that a box containing 15 oranges out of which 12 are good and 3 are bad ones will be approved for sale.\\
	\solution
\input{ncert/12/13/2/3/multinom.tex}
\item A box contains 3 orange balls, 3 green balls and 2 blue balls. Three balls are drawn at random from the box without replacement. The probability of drawing 2 green balls and one blue ball is
\begin{enumerate}
\item $\frac{3}{28}$\\
\item $\frac{2}{21}$\\
\item $\frac{1}{28}$\\
\item $\frac{167}{168}$
\end{enumerate}
%\input{exemplar/12/13/3/79/main.tex}
\item %\input{exemplar/12/13/3/74/main.tex}
\item A bag contains 5 red and 3 blue balls. If 3 balls are drawn at random without replacement the probability that exactly two of the three balls were red, the first ball being red is\\
%\input{exemplar/12/13/3/75/main.tex}
    \end{enumerate}
